---
title: "Imputed QCEW Datasets"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Setup
```{r message = F}
library(tidyverse)
library(furrr)
 
qcew_imputed = readRDS("./data/QCEW_imputations_20211006.Rds")
```

## 2.Data Structure

The list `qcew_imputed` contains 10 imputed QCEW datasets:
```{r}
print(names(qcew_imputed))
```

Each imputed QCEW dataset is of size `r nrow(qcew_imputed[[1]])` by `r ncol(qcew_imputed[[1]])`.

Each row is an industry, there are `r nrow(qcew_imputed[[1]])` industries.

Each row has employment data for the following 20 quarters:
```{r}
print(colnames(qcew_imputed$`imputation-1`)[-c(1,2)])
```

Here is a piece of the dataset:
```{r}
head(qcew_imputed$`imputation-1`, 10)
```

## 3.Use of Data

We can do loops:
```{r eval = FALSE}
result = NULL
for (item in names(qcew_imputed)) {
  result[[item]] = MyAnalysis(qcew_imputed[item])
}
```

or use future map for parallel compute:
```{r eval = FALSE}
result = qcew_imputed %>% 
  future_map(
    ~{
      data = .
      MyAnalysis(data)
    }
  )
```

Once the analysis is done, we pool the results using Robin's rule:
```{r eval = FALSE}
final_result = PoolResult(result)
```

